Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-11 ms.tex
showing comparisons w/ flat fielding of OTIS data

\subsubsection{Pass and a Half Grism Time Series Test}
The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
The telescope is suspended vertically and can potentially swing under these vibrations.

@@

@@

>>>>

\subsubsection{Pass and a Half Grism Time Series Test - Photometry}
The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests that simultaneously illuminated the short wavelength and long wavelength channels.
The ``O9'' supercontinuum illuminated the detector over a wide wavelength range from 2.5 to 4.1$\mu$m.
A small fraction of the light is emitted at wavelengths shorter than 2.5 $\mu$m, which is sufficient to illuminate the short wavelength detector to peak counts of $\sim 260$DN per exposure.
Meanwhile, the peak of the grism is $\sim$ 26,000 DN.
This lamp configuration was a pass and a half test, which suffered from the vibrations and oscillations of the suspension system, which can be perturbed by motors such as vacuum pumps.
The telescope is suspended vertically and can potentially swing under these vibrations.

@@

\subsubsection{Pass and a Half Grism Time Series Test - Spectroscopy}

@@

We also analyze the spectroscopic time series for the OTIS grism time series.
The extracted spectrum and dynamic spectrum (how it varies in time) can be seen in Figure \ref{fig:otisLWdynSpec}.
Flat fielding is important for removing the imprint of the crosshatch pattern, as visible in Figure \ref{fig:otisLWflatVsNoFlat}.

\begin{figure*}
\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
}\label{fig:otisLWflatVsNoFlat}
\end{figure*}
